Robust Trajectory Optimization on a Quantum System

### 2021-02-09 paper/4longitude.tex
resolved danny edits

\section{Depolarization Mitigation\label{sec:longitude}}
In this section, we outline a method
for optimizing the flux to mitigate depolarization.
For many superconducting circuits, the 1/$e$ depolarization time ($T_{1}$) is independent of the control parameters,
so the fastest possible gate incurs the least depolarization error
\cite{schulteherbruggen2011optimal}.
For the fluxonium, however, $T_{1}$ is strongly dependent on the flux.
We enable the optimizer to trade longer gate times
for lower depolarizaiton times or vice-versa by making the gate time a decision variable.
Additionally, previous work has modeled the gate error due to depolarization
by evolving density matrices under a master
equation \cite{rembold2020introduction, schulteherbruggen2011optimal}
or evolving a large number of states in a quantum trajectory approach
\cite{abdelhafez2019gradient}.
We avoid the increase in computational complexity required for these
techniques by penalizing the integrated depolarization rate in optimization.
Using this metric as a proxy for the gate error incurred
is reasonable because depolarization errors are incoherent and therefore
increase monotonically in time without interference.

The integrated depolarization rate is given by,
\begin{equation}
  D_{1}(t) = \int_{0}^{t} T_{1}^{-1}(a(t^{\prime})) dt^{\prime}.
\end{equation}
This value is appended to the augmented state \eqref{eq:astatecontrols}
and its norm is penalized in the objective \eqref{eq:costfun} by setting
the corresponding element of the final augmented state to zero.
$T_{1}(a_{k})$ is obtained at each knot point by evaluating
a spline fit to experimental data of the form $\{(a, T_{1})\}$,
see Figure \ref{fig:longitudeb}.
It is also possible to fit a spline to theoretically obtained data.
However, experimental data often deviates from theoretical predictions
because it is difficult to account for all loss channels \cite{zhang2020universal},
and $T_{1}$ values often fluctuate on hour
time scales \cite{klimov2018fluctuations}.
\todo{You could cut this - starting from "It is also" to end of paragraph -
  no need to justify using experimental data if you've got it!
  Maybe just cite where the data is coming from, if published.}

We allow the optimizer to tune the gate time by
making the time step between each knot point
a decision variable. 
The square root of the time step $\sqrt{\Delta t_{k}}$
is appended to the augmented control \eqref{eq:astatecontrols}
and its square $\lvert \Delta t_{k} \rvert$ is used
for numerical integration in the discrete dynamics function \eqref{eq:dyn_con}.
To ensure numerical
integration accuracy is maintained, we constrain
the bounds of the time step at each knot point.
We promote the time steps
to decision variables, rather
than the number of knot points $N$, to ensure each cost function depends
only on the augmented state and augmented
controls at its own knot point $\ell_{k}(x_{k}, u_{k})$, which is necessary for iLQR.

We analyze the effect of depolarization on
the $X/2$, $Y/2$, and $Z/2$ gates obtained with
our numerical method and the analytic gates. We
use the Lindblad master equation to simulate $T_{1}$ dissipation for successive
gate applications, and compute the cumulative gate error
after each application, see Appendix \ref{appendix:longitude}.
The gate error reported in this text is the infidelity
of the evolved state and the target state averaged over 1000 pseudo-randomly
generated initial states.
The flux pulses for the numerical gates
are approximately periodic
with amplitudes $\sim 0.2 \textrm{GHz}$, see Figure \ref{fig:longitudea}.
They are reminiscent of the analytically determined Floquet operations
for a fluxonium described in \cite{huang2020engineering}
and realized in \cite{mundada2020floquet}.
The numerical gate times are greater
than the analytic gate times, but the
numerical flux pulses
spend more time at higher amplitudes, achieving higher $T_{1}$ times.
The single gate errors for both the analytic and numerical gates are
less than $10^{-4}$, which makes them sufficient for quantum error correction--a
prerequisite for fault-tolerant quantum
computing \cite{aharonov2008fault, knill2005quantum, gottesman1997stabilizer}.
However, the numerical gates achieve single gate errors
$\sim 5$ times less than those for the analytic gates,
which tracks closely with their relative improvement
on the integrated depolarization rate metric, see Appendix \ref{appendix:longitude}.
This single gate error advantage corresponds to a significant reduction in error correction resources
\todo{this seems like a strong statement - citation?}.
Furthermore, for successive gate applications, the gate error due to depolarization is approximately linear
in the gate count, which we expect for $t \ll T_{1}$, see Figure \ref{fig:longitudec}.
The gate error reduction for large gate counts is important for noisy, intermediate-scale quantum (NISQ)
applications. These improvements are significant for the constraints we have imposed on the gates,
and do not represent a fundamental limit to the optimization methods we have employed.

>>>>

\section{Depolarization Mitigation\label{sec:longitude}}
In this section, we outline a method
for optimizing the flux to mitigate depolarization.
For many superconducting circuits, the 1/$e$ depolarization time
($T_{1}$) is independent of the control parameters,
so the fastest possible gate incurs the least depolarization error
\cite{schulteherbruggen2011optimal}.
For the fluxonium, however, $T_{1}$ is strongly dependent on the flux.
We enable the optimizer to trade longer gate times
for longer $T_{1}$ times, or shorter $T_{1}$ times for shorter gate times,
by making the gate time a decision variable.
Additionally, previous work has modeled the gate error due to depolarization
by evolving density matrices under a master
equation \cite{rembold2020introduction, schulteherbruggen2011optimal},
or evolving a large number of states in a quantum trajectory approach
\cite{abdelhafez2019gradient}.
We avoid the increase in computational complexity required for these
techniques by penalizing the integrated depolarization rate in optimization.

The integrated depolarization rate is given by,
\begin{equation}
  D_{1}(t) = \int_{0}^{t} T_{1}^{-1}(a(t^{\prime})) dt^{\prime}.
\end{equation}
This value is appended to the augmented state \eqref{eq:astatecontrols}
and its norm is penalized in the objective \eqref{eq:costfun} by setting
the corresponding element of the final augmented state to zero,
which has the effect of incentivizing long $T_{1}$ times at each knot point.
$T_{1}(a_{k})$ is obtained at each knot point by evaluating
a spline fit to experimental data of the form $\{(a, T_{1})\}$,
see Figure \ref{fig:longitudeb}.
Using the integrated depolarization rate as a proxy for the gate error incurred
is reasonable because depolarization errors are incoherent and therefore
increase monotonically in time without interference.
Additionally, a master equation approach would require adding
density matrices of size $n \times n$
to the augmented state, and a quantum trajectory approach
would require adding many states of size $n$ to the augmented state,
where $n$ is the dimension of the Hilbert space.
The integrated depolarization rate is a single
real number; thus, the computational complexity of this
depolarization model does not scale
with the dimension of the Hilbert space.

We allow the optimizer to tune the gate time by
making the time step between each knot point
a decision variable \cite{howell2019altro}. 
The square root of the time step $\sqrt{\Delta t_{k}}$
is appended to the augmented control \eqref{eq:astatecontrols}
and its square $\lvert \Delta t_{k} \rvert$ is used
for numerical integration in the discrete dynamics function \eqref{eq:dyn_con}.
To ensure numerical
integration accuracy is maintained, we constrain
the bounds of the time step at each knot point.

We analyze the effect of depolarization on
the $X/2$, $Y/2$, and $Z/2$ gates obtained with
our numerical method and the corresponding analytic gates. We
use the Lindblad master equation to simulate $T_{1}$ dissipation for successive
gate applications, and compute the cumulative gate error
after each application, see Appendix \ref{appendix:longitude}.
The gate error reported in this text is the infidelity
of the evolved state and the target state averaged over 1000 pseudo-randomly
generated initial states.

The flux pulses for the numerical gates
are approximately periodic
with amplitudes $\sim 0.2 \textrm{GHz}$, see Figure \ref{fig:longitudea}.
They are reminiscent of the analytically determined Floquet operations
for a fluxonium described in \cite{huang2020engineering}
and realized in \cite{mundada2020floquet}.
The numerical gate times are greater
than the analytic gate times, but the
numerical flux pulses
spend more time at higher flux values, achieving higher $T_{1}$ times on average,
see Figure \ref{fig:longitudeb}.
The single gate errors for both the analytic and numerical gates are
less than $10^{-4}$, which makes them sufficient for quantum error correction--a
prerequisite for fault-tolerant quantum
computing \cite{aharonov2008fault, knill2005quantum, gottesman1997stabilizer}.
However, the numerical gates achieve single gate errors
$\sim 5$ times less than those for the analytic gates,
which tracks closely with their relative improvement
on the integrated depolarization rate metric, see Appendix \ref{appendix:longitude}.
This single gate error advantage corresponds to a
significant reduction in error correction resources
\cite{paetznick2014resource, suchara2013comparing}.
Furthermore, for successive gate applications,
the gate error due to depolarization is approximately linear
in the gate count, which we expect for $t \ll T_{1}$, see Figure \ref{fig:longitudec}.
The gate error reduction for large gate counts is
important for noisy, intermediate-scale quantum (NISQ)
applications. These improvements are significant for the constraints
we have imposed on the gates,
and do not represent a fundamental limit to the optimization
methods we have employed.

### 2021-02-09 paper/5static.tex
resolved danny edits

\section{Robustness to Static Parameter Uncertainty \label{sec:static}}
We have formulated the QOC
problem as an open-loop optimization problem--equivalently,
we do not incorporate feedback from the experiment in optimization.
However, the device's parameters deviate from the parameters we use in optimization,
leading to poor experimental performance. We combat errors
of this form using robust control techniques,
making the state evolution insensitive
to parameter uncertainty. As an example,
we mitigate errors arising from the drift and finite measurement
precision of the qubit frequency which modifies the fluxonium Hamiltonian
\eqref{eq:hamiltonian} by $f_{q} \rightarrow f_{q} + \delta f_{q}$.
We consider three robust control techniques to accomplish this task:
a sampling method, an unscented sampling method,
and a derivative method.

@@

Whereas the sampling method penalizes the deviations of the sample states
from the target state, the unscented sampling method
penalizes the deviations of the sample states from the nominal state
\cite{howell2020direct, lee2013sigma,
  thangavel2020robust}. Accordingly, the cost function we add
to the objective \eqref{eq:costfun} takes the form
$\sum_{k, j} c_{k} (\psi^{j}_{k} - \psi_{k})^{T}
(\psi^{j}_{k} - \psi_{k})$, where $c_{k}$ is a
constant we supply, $\psi_{k}$ is
the evolved initial state (nominal state), and $\psi^{j}_{k}$ is a sample state
that evolves under a modified Hamiltonian similar to that in the sampling method.
We omit bra-ket notation here to emphasize that
the states are real vectors, and are given by the right-hand-side of the
isomorphism \eqref{eq:isomorphism}. Additionally,
the unscented sampling method employs the unscented transform
\cite{julier2004unscented, uhlmann1995dynamic}
to prevent the sample states
from drifting too far or close to the nominal state during evolution,
which would result in exceedingly large or small deviations in the cost function.
In particular, the sample states are chosen to encode a unimodal distribution over
the $2n$ elements of the nominal state, modeling the uncertainty in the state
as a result of the uncertainty in the parameter. The unscented transform
accurately propagates the mean and covariance of this distribution between
knot points, or equivalently, through the transformation of the TDSE.
For this method, we sample on one initial state $(\ket{0} + i\ket{1}) / \sqrt{2}$,
and do not observe a performance increase
using more initial states, for example those from the operator basis.
A detailed procedure for the unscented transformation is given
in Appendix \ref{appendix:unscented}.

The derivative method penalizes the sensitivity of the state
to the uncertain parameter, which is encoded in the $l$\textsuperscript{th}-order
state derivative $\partial_{f_{q}}^{l} \ket{\psi}$. In the $m$\textsuperscript{th}-order
derivative method, we append all state derivatives of order $1, \dots, m$
to the augmented state vector \eqref{eq:astatecontrols}
for each initial state. We use the initial state $\ket{0}$ for this method,
and observe no advantage to using more initial states.
We penalize the norms of the state derivatives
in the objective \eqref{eq:costfun} by setting the corresponding elements
of the final augmented state to zero.
We could obtain the state derivatives at each knot point
with backward-mode differentiation.
In a naive automatic differentiation scheme,
the discrete dynamics function at knot points
$1, \dots, k - 1$ would be differentiated to obtain the state
derivative at knot point $k$, requiring
$O(N^{2})$ matrix multiplications. Instead, we 
employ forward-mode differentiation on the TDSE \eqref{eq:tdse}
to obtain coupled, first-order ODEs
which require $O(N)$ matrix multiplications to integrate.
For example, the dynamics for the $1$\textsuperscript{st}-order derivative method are:
\begin{align}
  i \hbar \frac{d}{dt} \ket{\psi} &= H \ket{\psi},\\
  i \hbar \frac{d}{dt} \ket{\partial_{f_{q}}\psi} &=
  H \ket{\partial_{f_{q}} \psi} +
  (\partial_{f_{q}} H) \ket{\psi}.
  \label{eq:d1dyn}
\end{align}
We integrate the coupled ODEs with exponential
integrators, see Appendix \ref{appendix:derivative},
in the discrete dynamics function \eqref{eq:dyn_con}. For runtimes
of the three robust control techniques,
consult Appendix \ref{appendix:time}.

@@

The analytic gate corresponds to
idling at the flux frustration point $a_{k} = 0 \ \forall \ k$, see Figure
\ref{fig:statica}. Its gate time $1 / 4 f_{q} \sim 18\textrm{ns}$
is the shortest possible for a $Z/2$ gate on the device.
The gate's erroneous rotation angle
$2 \pi \delta f_{q} / 4 f_{q}$ is linear in the
qubit frequency detuning, resulting in a gate error that is quadratic
in the detuning.
At a one-percent
detuning ($\lvert \delta f_{q} \rvert / f_{q} = 1\%$),
the gate error is $\sim 4.5 \cdot 10^{-5}$,
which is sufficient for quantum error correction.
Although the gate performs well, it cannot be extended
to gate times other than
$1 / 4 f_{q}$. The ability to perform
phase gates in any given time is critical
for multi-qubit experiments, where the qubits operate at different
frequencies $f_{q, i} \neq f_{q, j}$.
We can find solutions using the numerical methods at
all gate times above $18$ns, see Figure \ref{fig:staticb}.
These numerical methods offer an effective scheme for synchronizing
multi-qubit experiments.

The flux pulse produced by the sampling method
transitions  smoothly away from idles at the flux frustration point,
whereas that for the unscented sampling method employs
three distinct transitions.
The gate error at a one-percent qubit frequency detuning for the sampling method
does not improve substantially over the
range of gate times. Conversely, the gate error at a one-percent detuning
for the unscented sampling method reaches a minimum of $\sim 3.9 \cdot 10^{-5}$
near fractions of the Larmor period $2/4f_{q} \sim 36\textrm{ns},
3/4f_{q} \sim 54\textrm{ns}, 4/4f_{q} \sim 72\textrm{ns}$.

The two derivative methods converge on qualitatively similar flux pulses that
use fast triangle pulses at the boundaries and idle near the flux frustration point,
similar to the flux pulse produced by the unscented sampling method.
The gate errors at a one-percent qubit frequency detuning
for both derivative methods decrease super-linearly in their gate times.
The 2\textsuperscript{nd}-order method does not offer a substantial improvement
over the 1\textsuperscript{st}-order method for most gate times.
The gate error at a one-percent detuning for the 1\textsuperscript{st}-order
method reaches $10^{-7}$ at the Larmor period $1 / f_{q} \sim 72$ns,
see Figure \ref{fig:staticc}.
This result mimics the
ability of composite pulses to mitigate parameter uncertainty errors to arbitrary
order with sufficiently many pulses \cite{merrill2014progress}.
It is difficult to choose an appropriate composite pulse
for the problem studied here due to our Hamiltonian and experimental constraints.
We propose comparisons between composite pulses and numerical techniques
for future work.

%% F3
\begin{figure*}[ht]
  \begin{subfigure}{.4\textwidth}
    \includegraphics[width=\linewidth]{assets/f3a.png}
    \caption{}
    \label{fig:stochastica}
  \end{subfigure}\hspace{0.05\textwidth}
  \begin{subfigure}{.4\textwidth}
    \includegraphics[width=\linewidth]{assets/f3b.png}
        \caption{}
    \label{fig:stochasticb}
  \end{subfigure}
  \caption{
    (a) Flux pulses for $X/2$ gates robust to flux offsets
    constructed with the analytic (A),
    sampling (S), unscented sampling (U), and the 1\textsuperscript{st}-
    and 2\textsuperscript{nd}-order derivative methods (D1, D2).
    (b) Cumulative gate error due to 1/$f$ flux noise for
    successive gate applications. The cumulative gate errors for the
    sampling, unscented sampling, and the derivative methods are indistinguishable.
  }
  \label{fig:stochastic}
\end{figure*}

>>>>

\section{Robustness to Static Parameter Uncertainty \label{sec:static}}
We have formulated the QOC
problem as an open-loop optimization problem; equivalently,
we do not incorporate feedback from the experiment in optimization.
However, the device's parameters deviate from the parameters we use in optimization,
leading to poor experimental performance. We combat errors
of this form using robust control techniques,
making the state evolution insensitive
to parameter uncertainty. As an example,
we mitigate errors arising from the drift and finite measurement
precision of the qubit frequency, which modifies the fluxonium Hamiltonian
\eqref{eq:hamiltonian} by $f_{q} \rightarrow f_{q} + \delta f_{q}$.
We consider three robust control techniques to accomplish this task:
a sampling method, an unscented sampling method,
and a derivative method.

@@

Whereas the sampling method penalizes the deviations of the sample states
from the target state, the unscented sampling method
penalizes the deviations of the sample states from the nominal state
\cite{howell2020direct, lee2013sigma,
  thangavel2020robust}. Accordingly, the cost function we add
to the objective \eqref{eq:costfun} takes the form
$\sum_{k, j} c_{k} (\psi^{j}_{k} - \psi_{k})^{T}
(\psi^{j}_{k} - \psi_{k})$, where $c_{k}$ is a
constant we supply, $\psi_{k}$ is
the evolved initial state (nominal state), and $\psi^{j}_{k}$ is a sample state
that evolves under a modified Hamiltonian similar to that in the sampling method.
We omit bra-ket notation here to emphasize that
the states are real vectors and are given by the right-hand-side of the
isomorphism \eqref{eq:isomorphism}.
The sample states are chosen to encode a unimodal distribution over
the $2n$ elements of the nominal state, modeling the uncertainty in the state
as a result of the uncertainty in the parameter. We use the unscented transform
\cite{julier2004unscented, uhlmann1995dynamic}
to accurately propagate the mean and covariance of this distribution between
knot points, or equivalently, through the transformation of the TDSE \eqref{eq:tdse}.
Unlike the sampling method, the cost function for the unscented sampling method
is sensitive to global phases. Accordingly, we
do not observe a performance increase when
using more than one initial state. 
A detailed procedure for the unscented transformation is given
in Appendix \ref{appendix:unscented}.

The derivative method penalizes the sensitivity of the state
to the uncertain parameter, which is encoded in the $m$\textsuperscript{th}-order
state derivative $\ket*{\partial_{f_{q}}^{m} \psi} \equiv \partial_{f_{q}}^{m} \ket*{\psi}$.
In the $m$\textsuperscript{th}-order
derivative method, we append all state derivatives of order $1, \dots, m$
to the augmented state vector \eqref{eq:astatecontrols}
for each initial state.
We obtain the state derivatives at each knot point by performing forward-mode
differentiation on the TDSE \eqref{eq:tdse}.
For example, the dynamics for the $1$\textsuperscript{st}-order derivative method are:
\begin{align}
  i \hbar \frac{d}{dt} \ket{\psi} &= H \ket{\psi},\\
  i \hbar \frac{d}{dt} \ket{\partial_{f_{q}}\psi} &=
  H \ket{\partial_{f_{q}} \psi} +
  (\partial_{f_{q}} H) \ket{\psi}.
  \label{eq:d1dyn}
\end{align}
We integrate the coupled ODEs with exponential
integrators in the discrete dynamics function \eqref{eq:dyn_con},
see Appendix \ref{appendix:derivative}.
While the state $\ket*{\psi}$ has unit norm,
the state derivatives $\ket*{\partial^{m}_{f_{q}} \psi}$ need not, as is evident
from the non-unitary dynamics \eqref{eq:d1dyn}.
We penalize the norms of the state derivatives
in the objective \eqref{eq:costfun} by setting the corresponding elements
of the final augmented state to zero. Intuitively, this corresponds to penalizing
the sensitivity of each state element to the uncertain parameter. As was the case for
the unscented sampling
method, we do not observe a performance increase when using more than one initial state
for the derivative method.
For runtimes of the three robust control techniques,
consult Appendix \ref{appendix:time}.

@@

The analytic gate corresponds to
idling at the flux frustration point $a_{k} = 0 \ \forall \ k$, see Figure
\ref{fig:statica}. Its gate time $1 / 4 f_{q} \sim 18\textrm{ns}$
is the shortest possible for a $Z/2$ gate on the device.
The gate's erroneous rotation angle
$2 \pi \delta f_{q} / 4 f_{q}$ is linear in the
qubit frequency detuning, resulting in a gate error that is quadratic
in the detuning.
At a one-percent detuning ($\lvert \delta f_{q} \rvert / f_{q} = 1\%$),
the gate error is $\sim 4.7 \cdot 10^{-5}$,
which is sufficient for quantum error correction.

For the sampling method, the gate error at a one-percent qubit frequency detuning
does not decrease substantially over the
range of gate times, and begins to increase above $5 \cdot 10^{-5}$ for gate times
greater than $\sim 50$ns, see Figure \ref{fig:staticb}.
Optimization results for the sampling method reveal that it is typically
able to achieve a high fidelity for
one sample $\ket{\psi^{\pm}}$,
but not the other $\ket{\psi^{\mp}}$, indicating that it is difficult for the optimizer
to make progress on both objectives.
For the unscented sampling method,
the gate error at a one-percent detuning
does not decrease substantially 
over the gate times, but it does reach
a minimum of $\sim 3.9 \cdot 10^{-5}$
near fractions of the Larmor period $2/4f_{q} \sim 36\textrm{ns}$,
$3/4f_{q} \sim 54\textrm{ns}$, $4/4f_{q} \sim 72\textrm{ns}$.

%% F3
\begin{figure*}[ht]
  \begin{subfigure}{.4\textwidth}
    \includegraphics[width=\linewidth]{assets/f3a.png}
    \caption{}
    \label{fig:stochastica}
  \end{subfigure}\hspace{0.05\textwidth}
  \begin{subfigure}{.4\textwidth}
    \includegraphics[width=\linewidth]{assets/f3b.png}
        \caption{}
    \label{fig:stochasticb}
  \end{subfigure}
  \caption{
    (a) Flux pulses for $X/2$ gates robust to flux noise
    constructed with the analytic (A),
    sampling (S), unscented sampling (U), and the 1\textsuperscript{st}-
    and 2\textsuperscript{nd}-order derivative methods (D1, D2).
    (b) Cumulative gate error due to 1/$f$ flux noise for
    successive gate applications. The cumulative gate errors for the
    sampling, unscented sampling, and the derivative methods are indistinguishable.
  }
  \label{fig:stochastic}
\end{figure*}

The two derivative methods converge on qualitatively similar flux pulses that
idle near the flux frustration point and use fast triangle movements at the boundaries,
similar to the flux pulse produced by the unscented sampling method.
For both methods, the gate error at a one-percent qubit frequency detuning
decreases super-linearly in the gate time.
For the 1\textsuperscript{st}-order method, the gate error at a one-percent detuning 
reaches $10^{-7}$ at the Larmor period $1 / f_{q} \sim 72$ns,
see Figure \ref{fig:staticc}.
This result mimics the
ability of composite pulses to mitigate parameter uncertainty errors to arbitrary
order with sufficiently many pulses \cite{merrill2014progress}.
It is difficult to choose an appropriate composite pulse
for the problem studied here due to our Hamiltonian and experimental constraints.
We propose comparisons between composite pulses and numerical techniques
for future work.

Furthermore, the ability to perform
$Z$-type gates in any given time is critical
for synchronizing phases in multi-qubit experiments,
where the qubits have distinct
frequencies. Notably, the analytic gate studied here cannot be extended
to gate times other than $1 / 4 f_{q}$. 
We can find gates using the numerical methods at
all gate times above $18$ns, see Figure \ref{fig:staticb}.
These numerical methods offer an effective scheme for synchronizing
multi-qubit experiments.

### 2021-02-09 paper/6stochastic.tex
resolved danny edits

\section{Robustness to Time-Dependent Parameter Uncertainty \label{sec:stochastic}}
An additional source of experimental error arises from time-dependent
parameter uncertainty. For many flux-biased and inductively-coupled
superconducting circuit elements, magnetic flux noise is a significant
source of coherent errors. Flux noise
modifies the fluxonium Hamiltonian \eqref{eq:hamiltonian}
by $a(t) \rightarrow a(t) + \delta a(t)$.
The spectral density of the flux noise $\delta a(t)$ is observed to
follow a 1/$f$ distribution
\cite{bialczak20071f, koch2007model,
  yoshihara2006decoherence, yoshihara2010correlated},
so the noise is dominated by low-frequency components.
The analytic gate considered here
takes advantage of the low-frequency characteristic and
treats the noise as quasi-static, performing a generalization of the spin-echo
technique to compensate for erroneous drift \cite{hahn1952spin, meiboom1958modified}.

Additionally, we modify the robust control techniques presented
in the previous section to combat 1/$f$ flux noise.
The unscented sampling method is modified so that the sample states
are subject to 1/$f$ flux noise. The noise
is generated by filtering white noise sampled from a standard
normal distribution with a finite impulse response filter \cite{saspweb2011}.
The noise is then scaled by the 
flux noise amplitude of our device $A_{\Phi} = 5.21 \mu \Phi_{0} \implies
\sigma_{a} = 2.5 \cdot 10^{-5} \textrm{GHz}$.
In principle, we could modify the sampling method
similarly; however, we choose to subject the sample states
to static noise
$a(t) \rightarrow a(t) \pm \sigma_{a}$
for comparison. The derivative methods require no algorithmic modification
from the static case, but the TDSE is now differentiated with respect
to $a(t)$ instead of $f_{q}$ as in \eqref{eq:d1dyn}.

We analyze the gate errors due to 1/$f$ flux noise for
the $X/2$ gates constructed with the robust control techniques
and the analytic $X/2$ gate. To compute the gate error,
an initial state is evolved
under the fluxonium Hamiltonian \eqref{eq:hamiltonian}
where the optimized flux is modified $a(t) \rightarrow a(t) + \delta a(t)$.
The flux noise is generated as
we described for the unscented sampling method.
The reported gate error is the infidelity
averaged over $1000$ pseudorandomly generated initial states,
each of which is subject to a distinct pseudorandomly
generated flux noise instance.
To observe the effect of interfering coherent errors,
we simulate successive applications of the gate constructed by each method
and compute the cumulative gate error
after each application, see Figure \ref{fig:stochastic}.
Both the analytic
and numerical gates yield single gate errors
sufficient for quantum error correction.
Despite converging on qualitatively different solutions, the
numerical gates perform similarly in the concatenated
gate application comparison. Their gate errors
after $200$ gate applications $\sim 11 \mu\textrm{s}$ are
two orders of magnitude less than the gate error produced by the analytic gate.
1/$f$ flux noise is a significant source of coherent errors in NISQ applications and
these numerical techniques offer effective avenues to mitigate it.

>>>>

\section{Robustness to Time-Dependent Parameter Uncertainty \label{sec:stochastic}}
An additional source of experimental error arises from time-dependent
parameter uncertainty. For many flux-biased and inductively-coupled
superconducting circuit elements, magnetic flux noise is the dominant
source of coherent errors \cite{bialczak20071f, kakuyanagi2007dephasing,
  kumar2016origin, yoshihara2006decoherence}. Flux noise
modifies the fluxonium Hamiltonian \eqref{eq:hamiltonian}
by $a(t) \rightarrow a(t) + \delta a(t)$ where $\delta a(t)$ is the flux noise.
The spectral density of flux noise is observed to
follow a 1/$f$ distribution
\cite{bialczak20071f, koch2007model, kakuyanagi2007dephasing,
  kumar2016origin, yoshihara2006decoherence, yoshihara2010correlated,
  zhang2020universal},
so the noise is dominated by low-frequency components.
The analytic gate considered here
takes advantage of the low-frequency characteristic and
treats the noise as quasi-static, performing a generalization of the spin-echo
technique to compensate for erroneous drift \cite{hahn1952spin, meiboom1958modified}.

We modify the robust control techniques presented
in the previous section to combat 1/$f$ flux noise.
The unscented sampling method is modified so that the sample states
are subject to 1/$f$ flux noise. The noise
is generated by filtering white noise sampled from a standard
normal distribution with a finite impulse response filter \cite{saspweb2011}.
The noise is then scaled by the 
flux noise amplitude of our device $A_{\Phi} = 5.21 \mu \Phi_{0} \implies
\sigma_{a} = 2.5 \cdot 10^{-5} \textrm{GHz}$.
In principle, we could modify the sampling method
similarly; however, we choose to subject the sample states
to static noise
$a(t) \rightarrow a(t) \pm \sigma_{a}$
for comparison. The derivative methods require no algorithmic modification
from the static case, but the TDSE is now differentiated with respect
to $a(t)$ instead of $f_{q}$ as in \eqref{eq:d1dyn}.

We analyze the gate errors due to 1/$f$ flux noise for
the $X/2$ gates constructed with the robust control techniques
and the analytic $X/2$ gate. To compute the gate error,
we evolve an initial state
under the fluxonium Hamiltonian \eqref{eq:hamiltonian}
where the optimized flux is modified $a(t) \rightarrow a(t) + \delta a(t)$.
We generate the flux noise as
we described for the unscented sampling method.
The reported gate error is the infidelity
averaged over $1000$ pseudorandomly generated initial states,
each of which is subject to a distinct pseudorandomly
generated flux noise instance.
To observe the effect of interfering coherent errors,
we simulate successive applications of the gate constructed by each method;
we compute the cumulative gate error
after each application, see Figure \ref{fig:stochastic}.
Both the analytic
and numerical gates yield single gate errors
sufficient for quantum error correction.
Despite converging on qualitatively different solutions, the
numerical gates perform similarly in the concatenated
gate application comparison. Their gate errors
after $200$ gate applications $\sim 11 \mu\textrm{s}$ are
two orders of magnitude less than the gate error produced by the analytic gate.
1/$f$ flux noise is a significant source of coherent errors in NISQ applications,
and these numerical techniques offer effective avenues to mitigate it.

### 2021-02-09 paper/7conclusion.tex
jens edits 2 addressed or todo'd
resolved danny edits

\section{Conclusion}
We have applied state-of-the-art trajectory
optimization techniques to mitigate decoherence and
achieve robustness to parameter uncertainty
errors on a quantum system.
We have proposed a scheme for suppressing
depolarization with time-optimal
control and the depolarization probability model.
The computational cost of this model is
independent of the dimension of the Hilbert space, enabling
inexpensive optimization on high-dimensional quantum systems (hmm, this seems like something that definitely wasn't emphasized in the text - could be worth talking about this a little earlier. Also doesn't seem totally true right? Re Eq.(5)).
We have also proposed the derivative method for robust control which achieves
super-linear gate error reductions in the gate time for the static parameter
uncertainty problem we studied.
We have shown that the derivative, sampling, and unscented sampling methods
can mitigate 1/$f$ flux noise errors--which
dominate coherent errors for flux controlled qubits.
These robust control techniques can be applied
to any Hamiltonian,
allowing experimentalists in all domains to engineer robust
operations on their quantum systems.
These methods can be used to achieve the low gate errors
required for fault-tolerant quantum computing applications. Our
implementations of the techniques described in this work are available
at \url{https://github.com/SchusterLab/rbqoc}. \todo{static code?}

>>>>

\section{Conclusion}
We have applied state-of-the-art trajectory
optimization techniques to mitigate decoherence and
achieve robustness to parameter uncertainty
errors on a quantum system.
We have proposed a scheme for suppressing
depolarization with time-optimal
control and the integrated depolarization rate model.
The computational cost of this model is
independent of the dimension of the Hilbert space, enabling
inexpensive optimization on high-dimensional quantum systems.
We have also proposed the derivative method for robust control which achieves
super-linear gate error reductions in the gate time for the static parameter
uncertainty problem we studied.
We have shown that the derivative, sampling, and unscented sampling methods
can mitigate 1/$f$ flux noise errors--which
dominate coherent errors for flux controlled qubits.
These robust control techniques can be applied
to any Hamiltonian,
allowing experimentalists in all domains to engineer robust
operations on their quantum systems.
These methods can be used to achieve the low gate errors
required for fault-tolerant quantum computing applications. Our
implementations of the techniques described in this work are available
at \url{https://github.com/SchusterLab/rbqoc}. \todo{static code?}
